Master's Project Journal

### 2019-03-20 conf_paper/paper.tex
page 3 started

\section{FPGA Prototyping}
\subsection{FPGA Restrictions}
The use of an FPGA comes with many restrictions as to how a complex system such as an ADPLL can be designed with the mixed signal blocks, the DCO and phase detectors, in particular being curtailed by the lack of transistor level control of the design and layout.\\
Two potential solutions exist which alleviate this problem, and are suited to different frequency ranges and/or goals of the designer. Firstly the clock signal generated by the FPGA's clock distribution block can be used to drive accumulator based oscillators and phase detectors a technique suitable in two main use cases: The emulation of the performance of an already designed system operating at a proportionally cut down frequency. At frequencies that are orders of magnitude lower than the maximum obtainable clock frequency of the FPGA's clock manager.
The downside of this approach is that the minimum steps are dictated by the clock frequency of the FPGA, which at frequencies that are not orders of magnitude lower than the FPGA clock will result in coarse resolutions for detector or oscillator, and thus greater jitter seen at the oscillator output.\\
The second solution to the problem is more akin to the real world system, and uses the delay through primitive elements such as inverters, which can be deduced from measurements on the FPGA of choice but will vary depending on the layout selected. In the case of the FPGA used for this paper, a Xilinx Artix-7 (XC7A100T-1CSG324C) this delay is in the region of 300 picoseconds but varies depending on the routing between elements. This design is better suited to scenarios where the desired operating frequency is a significant fraction of the maximum usable clock of the FPGA or it is particularly desirable to have asynchronous behaviour in the system as in an ASIC. It is not suited to lower frequency designs as the number of inverters required will run into spacial constraints.
\subsection*{Digitally Controlled Oscillators on an FPGA}

>>>>

\section{FPGA Prototyping}
\subsection{FPGA Restrictions}
The use of an FPGA comes with many restrictions as to how a complex system such as an ADPLL can be designed with the mixed signal blocks, the DCO and phase detectors, in particular being curtailed by the lack of transistor level control of the design and layout.\\
Two potential solutions exist which alleviate this problem, and are suited to different frequency ranges and/or goals of the designer. Firstly the clock signal generated by the FPGA's clock distribution block can be used to drive accumulator based oscillators and phase detectors a technique suitable in two main use cases: The emulation of the performance of an already designed system operating at a proportionally cut down frequency. At frequencies that are orders of magnitude lower than the maximum obtainable clock frequency of the FPGA's clock manager.
The downside of this approach is that the minimum steps are dictated by the clock frequency of the FPGA, which at frequencies that are not orders of magnitude lower than the FPGA clock will result in coarse resolutions for detector or oscillator, and thus greater jitter seen at the oscillator output.\\
The second solution to the problem is more akin to the real world system, and uses the delay through primitive elements such as inverters, which can be deduced from measurements on the FPGA of choice but will vary depending on the layout selected. In the case of the FPGA used for this paper, a Xilinx Artix-7 (XC7A100T-1CSG324C) this delay is in the region of 300 picoseconds but varies depending on the routing between elements. This design is better suited to scenarios where the desired operating frequency is a significant fraction of the maximum usable clock of the FPGA or it is particularly desirable to have asynchronous behaviour in the system as in an ASIC. It is not suited to lower frequency designs as the number of inverters required will run into spacial constraints.
\subsection{Digitally Controlled Oscillators on an FPGA}
There are three key designs that be used to implement a DCO on an FPGA, two of which rely on the FPGA clock and one using inverter primitives. 
\subsubsection*{Design 1}
The first of these is a linear in period design using an accumulator architecture, with a variable reload value on overflow. Here the control code modifies the reload value around a bias point and thus adjusts the time taken for overflow to be reached with the oscillator's period given as $T_{osc} = (2^n - (\textrm{bias}+\textrm{code}))\times\textrm{clock period}$. Period linearity is a desirable characteristic as it mimics the behaviour of many mixed-signal implementations, and is the key use case of this method. The choice of output signal however highlights the drawbacks of this method. With the accumulator's MSB acting as the output less than half of the control codes are feasible. As the minimum period is set by the number of unused bits and the maximum period fixed at twice the minimum the frequency and tuning range combinations are very limited.
In addition the wave output by this oscillator is not infact square, but skewed by the bias point.
\subsubsection*{Design 2}
A linear in frequency design using an accumulator is also viable
